Luminance constancy under fixed geometry

### 2018-02-13 Draft2/draft2.tex
discussion

\section{Discussion} \label{Discussion}
In this paper, we studied luminance constancy using naturalistic images. We generated datasets of multispectral images labeled by the reflectance of a target object in each image. The images were generated using a software pipeline developed for this work that we call Virtual world color constancy (VWCC). The software creates 3D scene descriptors based on programatic information provided by the user. Such information include the shape of the 3D rendering space, the shape, size, position and material properties of the objects and light sources in the scene, the location of the observer, etc. We assign these geometrical and spectral properties (the power spectrum of the light sources and the surface reflectance of the objects) using random sampling from available databases of naturally occurring objects, light sources and surface reflectances. Thus, we generated a large database of labeled hyper-spectral images, with naturalistic scene properties, but with the information about the surface reflectance and illumination at every pixel in the image. Such databases are nearly impossible to generate for natural scenes as it is very hard to measure the surface reflectance of every object and the illumination at every point, even for well controlled scenes in a lab. We used these labeled images in a supervised manner to understand the computations required for estimating the luminance of an object under spectral variations in the scene.

In this work, as a first step towards understanding luminance constancy, we generated images labeled with the luminance of a target object. We performed four types of spectral manipulations in the scene while generating the images (Fig.~\ref{fig:introExampleFigure}-\ref{fig:studiedCases}). 1. variations in the surface reflectance spectrum of the target object, 2. variations in surface reflectance spectrum of both target and the background objects, 3. variations in the surface reflectance spectrum of the target and the emission spectrum of the light source, and 4. variation is surface reflectance spectrum of the target and the background objects and the emission spectrum of the light source. We generated hundreds of images at multiple luminance level of the target object for each of these cases. Then using a model of the early visual system, we generated the response of the cones in the retina for each image in our database. These model retinal responses, along with the luminance label of the images, were then used as the input to supervised learning algorithms. Using our supervised methods, we leant that the target object luminance can be obtained from simple manipulation of the cone response for case where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, the light source illumination spectra. In these cases, the luminance can be obtained by comparing the response of the cones corresponding to the target and the background objects. When all these three types of spectral variations are allowed simultaneously, one needs additional information to obtain the luminance of the target object.

>>>>

\section{Discussion} \label{Discussion}
In this paper, we studied luminance constancy using naturalistic images. We used a software pipeline called  Virtual world color constancy (VWCC), which was developed for this work, to generate datasets of multispectral images labeled by the luminance of a target object in each image. VWCC creates 2D multispectral images of 3D scenes based on information provided by the user. Such information include the shape of the 3D space, the shape, size, position and material properties of the objects and light sources in the scene. In our work, we assigned these geometrical and spectral properties using random sampling from available databases of natural objects and light sources. Thus, we generated a large database of labeled hyper-spectral images, with naturalistic scene properties, where we have the ground truth information about every surface and light source. Such databases, of even a few images, are nearly impossible to obtain for natural scenes. This is because it is very hard to measure the surface reflectance and the illumination spectrum at every point in a scene, even for well controlled lab environments.

We used the software generated labeled images in a supervised manner to understand luminance constancy under four types of spectral manipulations (Fig.~\ref{fig:introExampleFigure}-Fig.~\ref{fig:studiedCases}). We found that target object luminance can be recovered through simple manipulation of the retinal cone responses for cases where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, or the light source illumination spectra. When variations are allowed only in the target object surface reflectance spectrum, or only the target object and the background objects surface reflectance spectra, the luminance can be estimated directly from the response of retinal cone photoreceptors. If the background spectra is fixed, but the target object reflectance spectrum and the light source illumination spectra are varying, the luminance can be obtained from the contrast between the cone response corresponding to the target and the background. When all three spectral variations are allowed simultaneously, one needs additional information to obtain the target object luminance.
